`SCPCL000824` - Using `SingleR` for classification of tumor cells

### 2024-07-08 analyses/cell-type-ewings/exploratory_analysis/annotation_notebooks/SCPCS000492/SCPCL000824_singler-classification.Rmd

UpSetR::upset(UpSetR::fromList(tumor_cells), order.by = "freq") |> print()
```
Generally, it looks like there is a large group of cells that are identified as tumor regardless of the reference, with a few cells that are specifically tumor in only one or two references.

>>>>

UpSetR::upset(UpSetR::fromList(tumor_cells), order.by = "freq") |> print()
```

Generally, it looks like there is a large group of cells that are identified as tumor regardless of the reference, with a few cells that are specifically tumor in only one or two references.
